%% cv-us.tex
%
% Jason R. Blevins 
% Curriculum Vitae
%
% http://jrblevin.freeshell.org
%
% Copyright (C) 2004-2006 Jason Blevins <jrblevin@sdf.lonestar.org>
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents, however, I do ask that you
% please leave this notice and the above URL in the source code if you
% choose to redistribute this file.
%
% $Id: cv-us.tex,v 1.23 2006/06/21 00:14:55 jrblevin Exp $
%
%%---------------------------------------------------------------------------
%
% Notes:
%
% * To create a new page use
%   \newpage \opening
%
% * res.cls includes an \address{} command which can be used up to twice,
%   but my address is too long for the format it uses.
%
% * Alternate documentclass statement to put headings in margin:
%   \documentclass[margin,line,11pt,final]{res}
%
% * Can divide publication/presentation list into subsections by year:
%   \section{\bf\small\hspace{8mm}2006}
%
%%----------------------------------------------------------------------------
\documentstyle[hyperref, margin, line]{res}

\hypersetup{backref,pdfpagemode=Full,colorlinks=true,backref}

\addtolength{\oddsidemargin}{-0.45in}
\addtolength{\voffset}{-0.30in}
\addtolength{\textwidth}{1.00in} \addtolength{\textheight}{1.50in}

\renewcommand{\namefont}{\LARGE\emph}

%%===========================================================================%%

\begin{document}

%---------------------------------------------------------------------------
% Document Specific Customizations

% Make lists without bullets and with no indentation
\setlength{\leftmargini}{0em}
\renewcommand{\labelitemi}{}

% Use large bold font for printed name at top of pages
\renewcommand{\namefont}{\large\textbf}

\newcommand{\remove}[1]{}

%---------------------------------------------------------------------------

\name{Adam Vogel}

\begin{resume}
\begin{ncolumn}{2}
  Gates Building Room 124 & (217) 621-9287 \\
  353 Serra Mall& { av@cs.stanford.edu } \\
  Stanford, CA 94305 & { \verb+http://cs.stanford.edu/~av/+} \\
\end{ncolumn}

%---------------------------------------------------------------------------


\section{\bf Education}
\begin{formatb}
\title{l}\dates{r}\\
\employer{l}\location{r}\\
%\body\\
\end{formatb}

\title{\textbf{Stanford University}}
\dates{2008 -- August 2014}
\employer{Doctor of Philosophy in Computer Science}
\location{}
\begin{position}
\end{position}

\title{\textbf{University of Illinois at Urbana-Champaign}}
\dates{2003 -- 2007}
\employer{Bachelor of Science in Computer Science, Minor in Mathematics}
\location{3.9 GPA (4.0 scale)}
\begin{position}
\end{position}

\section{\bf Employment}

 \begin{format}
 \employer{l}\location{r}\\
 \title{l}\dates{r}\\
 \body\\
 \end{format}

 \title{Research Assistant}
 \employer{\textbf{Stanford University}}
 \location{Stanford, CA}
 \dates{September 2008 -- August 2014}
 \begin{position}
  Pioneered the application of multi-agent reinforcement learning to grounded language learning, with additional research in sentiment analysis, information extraction, and robotics. 
  Managed several teams of students, published 10 papers, and presented at international conferences. \remove{Java, Scala, Python, C++.}
 \end{position}

 \title{Research Intern}
 \employer{\textbf{Honda Research Institute}}
 \location{Mountain View, CA}
 \dates{June 2011 -- August 2011}
 \begin{position}
  Invented a technique to lower fuel consumption in hybrid vehicles by predicting driving routes using inverse reinforcement learning, awarded US patent 20140018985 A1.
  \remove{Java.}
 \end{position}

 \title{Teaching Assistant}
 \employer{\textbf{Stanford University}}
 \location{Stanford, CA}
 \dates{November 2011 -- May 2012}
 \begin{position}
 Led a team of five to develop automatically-graded programming assignments for the Stanford Natural Language Processing Coursera course, used by 40,000 students.
 \remove{Java and Python.}
 \end{position}

 \title{Research Programmer}
 \employer{\textbf{University of Illinois}}
 \location{Champaign, IL}
 \dates{December 2007 -- August 2008}
 \begin{position}
 Created a machine learning based context-sensitive spelling correction plugin for Firefox.  \remove{C++.}
 \end{position}

 \title{Research Engineer}
 \employer{\textbf{RiverGlass Inc.}}
 \location{Champaign, IL}
 \dates{May 2006 -- December 2007} 
 \begin{position}
	Designed and developed a machine learning based natural language
	processing tool to extract relationships between named 
	entities in text. \remove{Java and C++.}
 \end{position}

 \title{Software Developer}
 \employer{\textbf{Abbott Laboratories}}
 \location{Waukegan, IL}
 \dates{May 2005 -- Aug 2005}
 \begin{position}
Implemented a suite of tools to analyze contract system performance logs and improve uptime. \remove{Perl and COBOLOL.}
 \end{position}

\section{\textsc{Key Publications}}
\begin{itemize}
\item Adam Vogel, Max Bodoia, Christopher Potts, and Dan Jurafsky. Emergence of Gricean Maxims from Multi-Agent Decision Theory. NAACL 2013.
\item Kevin Reschke, Adam Vogel, and Dan Jurafsky. Generating Recommendation Dialogs by Extracting Information from User Reviews. ACL 2013.
\item Adam Vogel and Dan Jurafsky. Learning to Follow Navigational Directions. ACL 2010.
\end{itemize}

\section{Select Honors}
\begin{itemize}
\item National Science Foundation Graduate Research Fellowship, 2008
\item Computing Research Association Outstanding Undergraduate Award, Honorable Mention, 2006
\remove{\item Outstanding Intern Award, Abbott Laboratories, 2005}
\item Intel International Science and Engineering Fair Finalist, 2003
\remove{\item American Association for Artificial Intelligence Special Award Winner, 2003}
\end{itemize}



%%---------------------------------------------------------------------------%%



 \section{\bf Skills}
 \begin{itemize}
 \item Computer: Java, Scala, Python, C++, Perl, Matlab, git, \LaTeX, Amazon Mechanical Turk 
 \item Mathematical: Machine Learning, Probabilistic Graphical Models, Reinforcement Learning, Game Theory, Convex Optimization, Mathematical Logic, Graph Theory
 \end{itemize}


%%---------------------------------------------------------------------------%%

%\begin{center}
%\vspace{\fill}\ \newlin
%{\tiny \rm $ $RCSfile: cv-us.tex,v $ $ }
%{\tiny \rm $ $Date: 2006/06/21 00:14:55 $ $ }
%{\tiny \rm $ $Revision: 1.23 $ $ }
%\end{center}

\end{resume}

\end{document}

%%===========================================================================%%
